---
title: "Chilko growth exploration"
date: "November 20, 2020"
output: html_document
---

PUSH TO GIT TES T

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# set up
setwd("~/Documents/ANALYSIS/data")
library(tidyverse)
library(broom)      # for nested modelling
library(ggpubr)     # for stat_cor in fig4
library(egg)        # for ggarrange
library(reshape2)   # for matrix for plot3D
library(plot3D)     # for 3D histogram
library(xlsx)
library(openxlsx)

# PART 1: data sources -- 'smolt.abund.raw' always throws an error. if you re-start the R session and re-run this block, it will work. 
smolt.bio.yrs <- getSheetNames("Daily Length (1986-2015).xlsx")
smolt.abund.raw <- read.xlsx("Chilko summary all years.xlsx", sheet="Annual outmigration")
esc.raw <- read.xlsx("DFO Sockeye Escapement All Years (June 2020).xlsx", sheet="SKAll")
fecund.raw <- read.xlsx("Sockeye Fecundity Database(2019VerifiedBB).xlsx", sheet="Data")
psc.raw <- read.csv("PSC_master.csv")
fry.raw <- read.xlsx("FryDB(Verified2019BB).xlsx", sheet="FryData")
```

```{r, include=F}
# Chilko data summaries
smolt_bio_yrs <- data.frame(year=as.numeric(smolt.bio.yrs), val="smolt biodata")

smolt_abund_yrs <- data.frame(year=as.numeric(smolt.abund.raw$Smolt.migration.year[1:68]), val="smolt abundance")

fry_bio_yrs <- fry.raw %>% 
  filter(Stream=="Chilko") %>%
  summarize(year=unique(YEAR), val="fry length & weight") %>% 
  print()

esc_yrs <- esc.raw %>% 
  filter(CU.Name %in% c("Chilko - Summer", "Chilko - Early Summer"), !is.na(Total), !is.na(eff_fem)) %>%
  summarize(year=unique(Year), val="adult & ef esc") %>% 
  print()

fecund <- fecund.raw %>%
  filter(`Stock.Name(stream)`=="Chilko River", !is.na(Final.Fecundity)) %>%
  summarize(year=unique(Year), val="fecundity") %>% 
  print()

fecund_lengths <- fecund.raw %>% 
  filter(`Stock.Name(stream)`=="Chilko River", !is.na(Final.Fecundity), !is.na(Std.Length), Std.Length!=0.0) %>% 
  summarize(year=unique(Year), val="fecundity & length paired") %>%
  print()

age <- psc.raw %>% 
  filter(Stream_Shore%in%c("Chilko River", "Chilko Lake - South End", "Chilko Lake - North End"), TotalAge>=3, TotalAge<=5, Sex=="Female") %>% 
  summarize(year=unique(CollYear), val="age") %>% 
  print()

age_length <- psc.raw %>%
  filter(Stream_Shore%in%c("Chilko River", "Chilko Lake - South End", "Chilko Lake - North End"), TotalAge>=3, TotalAge<=5, POH!="0", POH!="#N/A",
    POH!="", STD!="0", STD!="#N/A", STD!="", Sex=="Female") %>% 
  summarize(year=unique(CollYear), val="age & length paired") %>%
  print()

alldat <- rbind(smolt_bio_yrs, smolt_abund_yrs, fry_bio_yrs, esc_yrs, fecund, fecund_lengths, age, age_length)
```

<br>

<br>

## Chilko data summary ##

--------

DFO StAD data on Chilko juvenile and adult sockeye (Figure 1):

* Smolt abundance at migration
* Smolt length at migration
* Smolt age at migration
* Smolt migration timing (daily totals) - this may exist at finer resolution too
* Fry abundance, age, and size (sparse data)
* Total adult spawner abundance
* Effective female spawner abundance
* Male and female spawner length
* Fecundity
* Adult age (total and freshwater)
* Water level (continuous) and temperature (during programs)

Smolt length and age and fry length and age are currently stored in data formats that would require considerable work to bring into a useable format, especially for historical data. 

```{r, echo=F, warning=F}
ggplot(alldat, aes(x=val, y=year, group=year)) +
  annotate("rect", ymin=1990, ymax=1993, xmin=-Inf, xmax=Inf, fill="red", alpha=0.5) + 
  geom_hline(yintercept=1988, linetype="solid", colour="red", size=1, alpha=0.5) +
  geom_point(size=2.7, shape=21, fill="gray60", colour="black", stroke=1.1) +
  scale_y_continuous(breaks=seq(1938,2020,by=5)) +
  labs(y="", x="")+
  coord_flip() +
  theme_bw() +
  theme(text = element_text(size=12, colour="black"),
    axis.text.x = element_text(angle=45, hjust=1))
```

Figure 1. DFO Stock assessment time series for Chilko data types. No sex information was collected in conjunction with 'age' data in 1952 hence the gap. Lake fertilization years are coloured red (1988, 1990-1993). 

<br> 

Other types of data that may be held elsewhere: 

* Smolt freshwater growth rate (otoliths, scales or recaptures?)
* Smolt weight
* Smolt fat score
* Smolt growth rate (otoliths, scales or recaptures?) 
    - Smolt fork length in Lower Fraser/SoG
* Smolt survival during migration
    - Smolt abundance in Lower Fraser/SoG
* Smolt misc physiology - swim performance, hormones, respirometry, etc.
* Total growth rate over life (otoliths, scales) - PSC does not record to this level for adults but possible it could be obtained
* Adult fat score
* Adult misc physiology - swim performance, hormones, respirometry, etc.
* Fry abundance
* Lake productivity/food availability (especially during fertilization experimental years) - likely patchy at best
* Predator abundance (proxy or estimate of mortality rate)

Other data sources might be accessed through Environmental Watch Program, Hinch Lab, Mission Downstream (Tadey) or Strait of Georgia (Neville) programs. 

<br>

### Other systems ###

Sparse fry data (Figure 2) and smolt data (below) exists for other systems if controls/comparisons are required:

* Cultus 1984, 1990-1991, 2000-2020
* Nautley 1999-2000, 2019
* South Thompson 2012-2013, 2016
* Historic (~1940-1950) Adams Lake, Bowron, Francois Lake, Horsefly, Lillooet Lake, Little River, Lower Shuswap, Portage Creek, Quesnel Lake, Seton Creek, South Thompson, Stuart Lake, Thompson

```{r, include=F}
fry_pops <- fry.raw %>% 
  group_by(Stream, YEAR) %>%
  summarize(n=n()) %>% 
  print()
```

```{r, echo=F, warning=F}
ggplot(fry_pops %>% filter(Stream!="Chilko"), aes(x=Stream, y=YEAR)) +
  geom_point(size=2.7, shape=21, fill="gray60", colour="black", stroke=1.1) +
  scale_y_continuous(breaks=seq(1938,2020,by=1)) +
  labs(y="", x="")+
  coord_flip() +
  theme_bw() +
  theme(text = element_text(size=12, colour="black"),
    axis.text.x = element_text(angle=45, hjust=1))
```

Figure 2. StA fry data excluding Chilko. 

<br>

<br>

<br>

```{r echo=F, include=F}
###################################################################################################################################################
###################################################################################################################################################
```


## Methods/overview ##

--------

```{r, echo=F, include=F}
setwd("~/Documents/ANALYSIS/data")

smolt.df <- read.csv("chilko_smolt_df.csv")
fry.df <- read.csv("chilko_fry_df.csv")
rec.df <- read.csv("chilko_rdev_df.csv")
efs.df <- read.csv("chilko_efs_df.csv")
lf.raw <- read.xlsx("chilko_smoltlength_timeseries.xlsx", sheet="lf_sub", detectDates=T)


############
# CLEANING #
############

#-------- Amend smolt df to only include age1 smolt data for simplicity
smolts_a1 <- smolt.df %>% 
  select(smolt_year, length_weightavg_age1, length_unweightavg_age1, length_unweightse_age1, age1_total, smolt_total) %>%
  print()

#-------- Lengh-frequency
lf <- lf.raw %>% 
  rename(date=Date,
    length_mm=`Length.(mm)`,
    age=Age,
    freq=Freq,
    sum_lf=`Sum.(L.X.F)`) %>%
  mutate(year = lubridate::year(date)) %>%
  mutate(yday = lubridate::yday(date)) %>%
  mutate_at("age", as.factor) %>%
  print()

# expand frequency table to be observations only (no 0 freq measurements)
lf_exp <- lf[rep(1:nrow(lf), lf[["freq"]]), ]


###################
# FOR 3D PLOTTING #
###################
# clean, pivot to wide matrix format 
lf_exp_w14_1 <- lf %>%
  filter(year==2014, age==1) %>%
  arrange(yday, length_mm) %>%
  select(yday, length_mm, freq) %>%
  pivot_wider(names_from=length_mm, values_from=freq) %>%
  column_to_rownames(var="yday") %>%
  print()

# replace 0s with NAs to make plot clearer
lf_exp_w14_1[lf_exp_w14_1==0]=NA

# convert to matrix format
lf_exp_w14_1 <- data.matrix(lf_exp_w14_1, rownames.force = NA)

# x and y value sequences for plot
rnameseq <- as.numeric(row.names(lf_exp_w14_1))
cnameseq <- as.numeric(colnames(lf_exp_w14_1))
```

The majority of smolts leave Chilko Lake as age-1 (>81% from 1986-2019). Unless noted, all analysis from here-on is limited to age-1 smolts.

```{r, echo=F, warning=F, include=F}
#Figure x. Proportion of age-1 smolts leaving Chilko over time.
ggplot(data=smolt.df %>% group_by(smolt_year) %>% summarize(propn_age1 = age1_total/(age1_total+age2_total)), 
        aes(x=smolt_year, y=propn_age1)) +
  geom_line(size=1, colour="gray80") +
  geom_point(shape=21, size=3.5, colour="black", fill="gray80", stroke=1.5) +
  scale_x_continuous(breaks=seq(1986,2020, by=2)) +
  scale_y_continuous(limits=c(0.80,1), breaks=seq(0.80,1.0,by=0.05)) +
  labs(x="", y="% Age-1 smolts") +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=10),
    axis.title = element_text(colour="black", size=12, face="bold"))
```

<br>

Given substantial variability in nightly smolt migration and the non-random method of obtaining smolt length samples, it is recommended that smolt lengths be weighted by nighly abundance (S. Decker). With the exception of a small number of data points, Figure 3 shows minimal difference between weighted and unweighted average smolt fork lengths each year.  

```{r, echo=F, warning=F}
#########
# FIG 3 #
#########
ggplot() +
  #annotate("text", x=2020, y=173, label="A") +
  annotate("rect", xmin=1990, xmax=1993, ymin=-Inf, ymax=Inf, fill="red", alpha=0.5) + 
  geom_vline(xintercept=1988, linetype="solid", colour="red", size=1, alpha=0.5) +
  geom_errorbar(data=smolts_a1, aes(x=smolt_year, ymin=length_unweightavg_age1-length_unweightse_age1, ymax=length_unweightavg_age1+length_unweightse_age1), width=0, size=1, colour="gray60") +
  geom_line(data=smolts_a1, aes(x=smolt_year, y=length_unweightavg_age1), colour="gray80", size=0.8, alpha=0.7) +
  geom_line(data=smolts_a1, aes(x=smolt_year, y=length_weightavg_age1), colour="black", size=0.8, alpha=0.7) +
  geom_point(data=smolts_a1, aes(x=smolt_year, y=length_unweightavg_age1), shape=21, colour="gray60", fill="gray80", size=2.5, stroke=1.2) +
  geom_point(data=smolts_a1, aes(x=smolt_year, y=length_weightavg_age1), shape=21, colour="black", fill="#00b8ff", size=2.5, stroke=1.2) +
  scale_x_continuous(limits=c(1986,2020), breaks=seq(1986,2020,by=3)) +
  scale_y_continuous(limits=c(70,100), breaks=seq(70,100,by=5))+
  labs(x="", y="Age-1 smolt length (mm)") +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=10),
    axis.title = element_text(colour="black", size=12, face="bold"))
```

*Figure 3. Age-1 Chilko smolt fork lenghts, unweighted (light gray), and weighted-by-abundace (blue). Red shaded areas indicate years of lake fertilization. Error bars indicate one standard error and are given only for unweighted data. Note 2015 is included for comparison but due to high water an RST was used in place of the fence, which may result in size-selective bias. Following 2014 a 3-day smoothing window was also applied to daily weighted and unweighted length calculations.*

<br>

In the most recent 5 years (fence not operated in 2015 and 2020) there is a significant effect of 'day' on average daily age-1 smolt length, and occasionally on age-2 daily average length as daily smolth lengths oscillate (Code 1 and Figure 4). However, there is no overall temporal trend in smolth length throughout the migration period (*R^2* < 0.12 for all ages and years; Figure 4). 

```{r, echo=F, warning=F, include=F}
### OLD FIG 4 - Daily smolt length (mm) in the most recent 5 years expressed as a) boxplot with medians and quartiles, and b) point size scaled by frequency of observations. Note different x- and y- axis limits for all plots.
ggplot(lf_exp%>%filter(!is.na(age)), aes(x=as.Date(yday, origin=as.Date("1970-01-01")), y=length_mm, group=interaction(age, yday))) +
  #geom_bar(stat="identity", colour="black") +
  #geom_point() +
  #geom_errorbar(aes(x=as.Date(yday, origin=as.Date("1970-01-01")), ymin=mean_length-sd, ymax=mean_length+sd)) +
  geom_boxplot(aes(fill=age), alpha=0.8, width=1) +
  scale_x_date(date_labels="%b %d") +
  labs(x="", y="Length (mm)") +
  facet_wrap(~year, scales="free") +
  theme_bw() +
  theme(legend.position = c(0.8,0.2))

ggplot(lf_exp%>%filter(!is.na(age)), aes(x=as.Date(yday, origin=as.Date("1970-01-01")), y=length_mm, size=freq, group=interaction(age, yday))) +
  geom_point(aes(fill=age), alpha=0.2, shape=21, stroke=0.5) +
  scale_x_date(date_labels="%b %d") +
  scale_size_continuous(range=c(2,8)) +
  labs(x="", y="Length (mm)") +
  facet_wrap(~year, scales="free") +
  theme_bw() +
  theme(legend.position = c(0.85,0.2),
    legend.box="horizontal") +
  guides(fill = guide_legend(override.aes = list(size = 3))) 
### OLD FIG 5 - Example 3-D plot of smolt length (mm) frequency over time during the 2014 outmigration. 
hist3D(x=rnameseq, y=cnameseq, z=lf_exp_w14_1, scale=F, expand=0.23, bty="g", phi=25,
        col=jet.col(100, alpha=1), border="black", shade=0, theta=40,
        space=0, ticktype="detailed", d=2, xlab = "Date", ylab = "Length (mm)", zlab = "Frequency", main="Chilko 2014")
```

```{r, warning=F, echo=F, message=F}
#########
# FIG 4 #
#########
ggplot(lf_exp%>%filter(!is.na(age)), aes(x=as.Date(yday, origin=as.Date("1970-01-01")), y=length_mm)) +
  geom_violin(aes(fill=age, group=interaction(age, yday))) +
  geom_smooth(aes(group=age, colour=age), method="lm") +
  stat_summary(aes(colour=age), fun=mean, geom="point") +
  labs(x="", y="Length (mm)") +
  facet_wrap(~year, scales="free") +
  theme_bw() +
  theme(legend.position = c(0.8,0.2)) +
  stat_cor(aes(group=age, colour=age, label=..rr.label..), size=3, label.y=c(67,67), label.x=c(108,120)) +
  stat_cor(aes(group=age, colour=age, label=..p.label..), size=3, label.y=c(60,60), label.x=c(108,120)) 
  
```

*Fig 4. Age-1 and -2 Chilko smolt length over time for most recent 5 years of data. Points indicate means. Violin widths indicate data density. Not different y-axis limits for each plot.*

<br>

*Code 1. Linear models examining the effect of 'day' on smolth length for each year and age.*

```{r, echo=F, warning=F, message=F}
lm1 <- lm(lf_exp[lf_exp$age=="1"&lf_exp$year=="2014",]$length_mm ~ lf_exp[lf_exp$age=="1" & lf_exp$year=="2014",]$date)
r1 <- resid(lm1)
hist(r1)    # slight skew, center weighted
qqnorm(r1)  # bit of a tail 
qqline(r1)
plot(r1)
plot(lm1)

# grouped anova/lm (toggle 'lm' / 'aov' function)
aovs <- lf_exp %>% 
  filter(!is.na(age)) %>%
  nest(-year, -age) %>% 
  mutate(fit = map(data, ~ lm(length_mm ~ date, data = .)),
         results = map(fit, glance)) %>% 
  unnest(results) %>%
  print()
```

<br>

<br>

<br>

## Size, abundance, and recruitment temporal trends ##

--------

Age-1 smolt size varied from approximately 70-100 over the history of the Chilko smolt program (Figures 6a). Lake fertilization was responsible for early size increases, but in recent years smolt fork length appears to become more variable (Figure 6a). Figure 4 shows trends in age-1 smolt length and recruitment. 

```{r, echo=F, warning=F, include=F}
##########
# FIG 6a #
##########
s1<-ggplot() +
  annotate("rect", xmin=1990, xmax=1993, ymin=-Inf, ymax=Inf, fill="red", alpha=0.5) + 
  geom_vline(xintercept=1988, linetype="solid", colour="red", size=1, alpha=0.5) +
  geom_line(data=smolts_a1, aes(x=smolt_year, y=length_weightavg_age1), colour="black", size=0.8, alpha=0.7) +  
  geom_point(data=smolts_a1, aes(x=smolt_year, y=length_weightavg_age1), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  scale_x_continuous(limits=c(1986,2020), breaks=seq(1986,2020,by=2)) +
  scale_y_continuous(limits=c(70,105)) +
  labs(x="", y="Smolt fork length (mm)") +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.text.x = element_text(angle=45, hjust=1),
    axis.title = element_text(colour="black", size=10, face="bold"))

##########
# FIG 6b #
##########
d<-ggplot() +
  annotate("rect", xmin=1990, xmax=1993, ymin=-Inf, ymax=Inf, fill="red", alpha=0.5) + 
  geom_vline(xintercept=1988, linetype="solid", colour="red", size=1, alpha=0.5) +
  geom_line(data=rec.df, aes(x=brood_year, y=rec_dev), colour="black", size=0.8, alpha=0.7) +  
  geom_point(data=rec.df, aes(x=brood_year, y=rec_dev), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  scale_x_continuous(limits=c(1986,2020), breaks=seq(1986,2020,by=2)) +
  scale_y_continuous(limits=c(-4,2)) +
  labs(x="", y="Recruitment deviates") +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.text.x = element_text(angle=45, hjust=1),
    axis.title = element_text(colour="black", size=10, face="bold"))

##########
# FIG 6c #
##########
a<-ggplot() +
  annotate("rect", xmin=1990, xmax=1993, ymin=-Inf, ymax=Inf, fill="red", alpha=0.5) + 
  geom_vline(xintercept=1988, linetype="solid", colour="red", size=1, alpha=0.5) +
  geom_line(data=efs.df, aes(x=efs_year, y=efs/1000), colour="black", size=0.8, alpha=0.7) +  
  geom_point(data=efs.df, aes(x=efs_year, y=efs/1000), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  scale_x_continuous(limits=c(1986,2020), breaks=seq(1986,2020,by=2)) +
  scale_y_continuous(limits=c(0,1300),  breaks=seq(0,1300,by=300)) +
  labs(x="", y="EFS (1000s)") +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.text.x = element_text(angle=45, hjust=1),
    axis.title = element_text(colour="black", size=10, face="bold")) 
```

```{r, warning=F, echo=F}
ggarrange(s1, d, a, nrow=3)
```

*Figure 6. a) Age-1 smolt fork length (weighted), b) Larkin model recruitment deviates, and c) effective female spawners over time.*

<br>

<br>

<br>



## Life history and recruitment ##

```{r, echo=F, include=F}
# data joins for plotting
fry.df <- fry.df %>% 
  mutate(smolt_year = fry_year+1) %>% 
  print()
smolt.fry.df <- left_join(smolts_a1, fry.df, by="smolt_year")

rec.df <- rec.df %>% 
  mutate(smolt_year=brood_year-2) %>%
  print()
smolt.rec.df <- left_join(smolts_a1, rec.df, by="smolt_year")

efs.df <- efs.df %>% 
  mutate(smolt_year = efs_year+2) %>% 
  print()
smolt.efs.df <- left_join(smolts_a1, efs.df, by="smolt_year")
smolt.efs.df <- smolt.efs.df %>%
  mutate(smolts_p_efs = age1_total/efs) %>% 
  print()
```

There is not a clear relationship between age-1 smolt size and the recruitment 2 years later. There is also not a clear relationship between the size of fry and age-1 smolts the following year (Figure 7).

```{r, echo=F, warning=F, include=F}
##########
# FIG 7a #
##########
ll<-ggplot() +
  annotate("text", x=29.4, y=103, label="A") +
  geom_point(data=smolt.fry.df, aes(x=fry_length_mean, y=length_weightavg_age1), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  #geom_text(data=smolt.fry.df, aes(x=fry_length_mean, y=length_weightavg_age1, label=smolt_year), nudge_x=0.1, nudge_y=0.8) +
  labs(x="Fry fork length (mm)", y="Age-1 smolt length (mm)") +
  scale_y_continuous(limits=c(70,105), breaks=seq(70,105,by=5))+
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.title = element_text(colour="black", size=10, face="bold"))

##########
# FIG 7b #
##########
lr<-ggplot() +
  annotate("text", x=99, y=1.75, label="B") +
  geom_point(data=smolt.rec.df, aes(x=length_unweightavg_age1, y=rec_dev), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  #geom_text(data=chilko.df, aes(x=length_unweightavg_age1, y=Dev, label=smolt_year), nudge_x=0.5, nudge_y=0.1) +
  labs(x="Age-1 smolt length (mm)", y="Recruitment deviates") +
  scale_y_continuous(limits=c(-4,2), breaks=seq(-4,2,by=1)) +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.title = element_text(colour="black", size=10, face="bold"))

##########
# FIG 7c #
##########
le<-ggplot() +
  annotate("text", x=1100, y=103, label="C") +
  geom_point(data=smolt.efs.df, aes(x=efs/1000, y=length_weightavg_age1), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  #geom_text(data=smolt.efs.df, aes(x=efs/1000, y=length_weightavg_age1, label=smolt_year), nudge_x=0.5, nudge_y=0.1) +
  labs(x="EFS (1000s)", y="Age-1 smolt length (mm)") +
  scale_y_continuous(limits=c(70,105), breaks=seq(70,105,by=5)) +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.title = element_text(colour="black", size=10, face="bold"))

##########
# FIG 7d #
##########
are<-ggplot() +
  annotate("text", x=1199, y=323, label="D") +
  geom_point(data=smolt.efs.df, aes(x=efs/1000, y=smolts_p_efs), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  #geom_text(data=chilko.df, aes(x=efs/1000, y=smolts_p_efs, label=smolt_year), nudge_x=0.5, nudge_y=0.1) +
  labs(x="EFS (1000s)", y="Age-1 smolts/EFS") +
  scale_y_continuous(limits=c(0,325), breaks=seq(0,325,by=50)) +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.title = element_text(colour="black", size=10, face="bold"))
```

```{r, echo=F, warning=F, message=F}
ggarrange(ll, lr, le, are, nrow=2, ncol=2)
```

*Figure 7. Relationship between a) fry length and age-1 smolt length (weighted) the following year, b) age-1 smolt length (weighted) and recruitment (deviates) two years later, c) brood-year effective female spawners and resulting age-1 smolt length (weighted) two years later, and d) brood-year effective female spawners and resulting age-1 smolts per effective female spawner two years later.*


