---
title: "Chilko growth exploration"
date: "Last update: `r Sys.Date()`"
output: 
  html_document: 
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(broom)      # for nested modelling
library(ggpubr)     # for stat_cor in fig4
library(egg)        # for ggarrange
library(reshape2)   # for matrix for plot3D
library(plot3D)     # for 3D histogram
library(readxl)
library(gitcreds)

# set up
gitcreds_set()
gitcreds_get()
setwd("~/ANALYSIS/data")

#--------- DATA: Part 1 summaries/trends 
smolt.df <- read.csv("chilko_smolt_df.csv")
fry.df <- read.csv("chilko_fry_df.csv")
rec.df <- read.csv("chilko_rdev_df.csv")
efs.df <- read.csv("chilko_efs_df.csv")
smolt.lf.raw <- read.csv("chilko_smolt_database_1986-2019_mar2021_LF.csv")

#--------- DATA: Part 2 von Bertalanffy growth/models
vb.dat <- read.csv("chilko_smolt_vb_database.csv") 
vb.fit.df <- read.csv("vonB_model_fits.csv")
vb.juviadult.fitdat <- read.csv("vonB_model_fits_data.csv")
vonB.fits.CIs <- read.csv("vonB_model_parameters.csv")

#--------- CLEANING
# Sometimes entered as 0s and sometimes as NAs, turn all NAs to 0 for consistency when expanding frequency table
smolt.lf <- smolt.lf.raw %>% 
  select(date:freq) %>%
  mutate(freq=ifelse(is.na(freq), 0, freq)) %>%
  mutate(date=lubridate::dmy(date)) %>%
  mutate(smolt_year=lubridate::year(date)) %>%
  mutate(yday=lubridate::yday(date)) %>%
  mutate_at("age", as.factor) %>%
  print()

# Expand LF data table 
smolt.lf <- smolt.lf[rep(1:nrow(smolt.lf), smolt.lf[["freq"]]), ]
```

<br>

### Temporal trends and life history patterns ###

Age-1 smolt size varied from approximately 70-100mm over the history of the Chilko smolt program (Figures 6a). Lake fertilization was responsible for early size increases, but in recent years smolt fork length appears to become more variable (Figure 6a). Figure 4 shows trends in age-1 smolt length and recruitment. 

```{r, echo=F, warning=F, include=F}
### FIGURE A: Age-1 length ~ time
length_temp<-ggplot() +
  annotate("rect", xmin=1990, xmax=1993, ymin=-Inf, ymax=Inf, fill="red", alpha=0.5) + 
  geom_vline(xintercept=1988, linetype="solid", colour="red", size=1, alpha=0.5) +
  geom_line(data=smolt.df, aes(x=smolt_year, y=length_weightavg_age1), colour="black", size=0.8, alpha=0.7) +  
  geom_point(data=smolt.df, aes(x=smolt_year, y=length_weightavg_age1), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  scale_x_continuous(limits=c(1986,2020), breaks=seq(1986,2020,by=2)) +
  scale_y_continuous(limits=c(70,105)) +
  labs(x="", y="Smolt fork length (mm)") +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.text.x = element_text(angle=45, hjust=1),
    axis.title = element_text(colour="black", size=10, face="bold"))

### FIGURE B: Recruitment deviates ~ time
rec_temp<-ggplot() +
  annotate("rect", xmin=1990, xmax=1993, ymin=-Inf, ymax=Inf, fill="red", alpha=0.5) + 
  geom_vline(xintercept=1988, linetype="solid", colour="red", size=1, alpha=0.5) +
  geom_line(data=rec.df, aes(x=brood_year, y=rec_dev), colour="black", size=0.8, alpha=0.7) +  
  geom_point(data=rec.df, aes(x=brood_year, y=rec_dev), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  scale_x_continuous(limits=c(1986,2020), breaks=seq(1986,2020,by=2)) +
  scale_y_continuous(limits=c(-4,2)) +
  labs(x="", y="Recruitment deviates") +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.text.x = element_text(angle=45, hjust=1),
    axis.title = element_text(colour="black", size=10, face="bold"))

### FIGURE C: EFS ~ time
efs_temp<-ggplot() +
  annotate("rect", xmin=1990, xmax=1993, ymin=-Inf, ymax=Inf, fill="red", alpha=0.5) + 
  geom_vline(xintercept=1988, linetype="solid", colour="red", size=1, alpha=0.5) +
  geom_line(data=efs.df, aes(x=efs_year, y=efs/1000), colour="black", size=0.8, alpha=0.7) +  
  geom_point(data=efs.df, aes(x=efs_year, y=efs/1000), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  scale_x_continuous(limits=c(1986,2020), breaks=seq(1986,2020,by=2)) +
  scale_y_continuous(limits=c(0,1300),  breaks=seq(0,1300,by=300)) +
  labs(x="", y="EFS (1000s)", caption="Figure . a) Age-1 smolt fork length (weighted), b) Larkin model recruitment deviates, and c) effective female spawners \nover time.") +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.text.x = element_text(angle=45, hjust=1),
    axis.title = element_text(colour="black", size=10, face="bold"),
    plot.caption = element_text(hjust=0, face="italic")) 
```

```{r, warning=F, echo=F}
ggarrange(length_temp, rec_temp, efs_temp, nrow=3)
```

<br>

```{r, echo=F, include=F}
# data joins for plotting
fry.df <- fry.df %>% 
  mutate(smolt_year = fry_year+1) %>% 
  print()
smolt.fry.df <- left_join(smolt.df, fry.df, by="smolt_year")

rec.df <- rec.df %>% 
  mutate(smolt_year=brood_year-2) %>%
  print()
smolt.rec.df <- left_join(smolt.df, rec.df, by="smolt_year")

efs.df <- efs.df %>% 
  mutate(smolt_year = efs_year+2) %>% 
  print()
smolt.efs.df <- left_join(smolt.df, efs.df, by="smolt_year")
smolt.efs.df <- smolt.efs.df %>%
  mutate(smolts_p_efs = age1_total/efs) %>% 
  print()
```

There is not a clear relationship between age-1 smolt size and the recruitment 2 years later. There is also not a clear relationship between the size of fry and age-1 smolts the following year (Figure 7).

```{r, echo=F, warning=F, include=F}
### FIGURE A: Age-1 length ~ fry length
sm_fr_length<-ggplot() +
  annotate("text", x=29.4, y=103, label="A") +
  geom_point(data=smolt.fry.df, aes(x=fry_length_mean, y=length_weightavg_age1), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  #geom_text(data=smolt.fry.df, aes(x=fry_length_mean, y=length_weightavg_age1, label=smolt_year), nudge_x=0.1, nudge_y=0.8) +
  labs(x="Fry fork length (mm)", y="Age-1 smolt length (mm)") +
  scale_y_continuous(limits=c(70,105), breaks=seq(70,105,by=5))+
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.title = element_text(colour="black", size=10, face="bold"))

### FIGURE B: Recruitment deviates ~ Age-1 length
rec_length<-ggplot() +
  annotate("text", x=99, y=1.75, label="B") +
  geom_point(data=smolt.rec.df, aes(x=length_unweightavg_age1, y=rec_dev), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  #geom_text(data=chilko.df, aes(x=length_unweightavg_age1, y=Dev, label=smolt_year), nudge_x=0.5, nudge_y=0.1) +
  labs(x="Age-1 smolt length (mm)", y="Recruitment deviates") +
  scale_y_continuous(limits=c(-4,2), breaks=seq(-4,2,by=1)) +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.title = element_text(colour="black", size=10, face="bold"))

### FIGURE C: Age-1 length ~ EFS
length_efs<-ggplot() +
  annotate("text", x=1100, y=103, label="C") +
  geom_point(data=smolt.efs.df, aes(x=efs/1000, y=length_weightavg_age1), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  #geom_text(data=smolt.efs.df, aes(x=efs/1000, y=length_weightavg_age1, label=smolt_year), nudge_x=0.5, nudge_y=0.1) +
  labs(x="EFS (1000s)", y="Age-1 smolt length (mm)", caption="Figure . Relationship between a) fry length and age-1 smolt length (weighted) the following year, b) age-1 smolt length (weighted) and recruitment (deviates) two years later, c) brood-year effective female spawners and resulting age-1 smolt length (weighted) two years later, and d) brood-year effective female spawners and resulting age-1 smolts per effective female spawner two years later.") +
  scale_y_continuous(limits=c(70,105), breaks=seq(70,105,by=5)) +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.title = element_text(colour="black", size=10, face="bold"),
    plot.caption = element_text(hjust=0,face="italic"))

### FIGURE D: Age-1 smolts/EFS ~ EFS 
sm_efs_efs<-ggplot() +
  annotate("text", x=1199, y=323, label="D") +
  geom_point(data=smolt.efs.df, aes(x=efs/1000, y=smolts_p_efs), shape=21, colour="black", fill="gray70", size=2.5, stroke=1.2) +
  #geom_text(data=chilko.df, aes(x=efs/1000, y=smolts_p_efs, label=smolt_year), nudge_x=0.5, nudge_y=0.1) +
  labs(x="EFS (1000s)", y="Age-1 smolts/EFS") +
  scale_y_continuous(limits=c(0,325), breaks=seq(0,325,by=50)) +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=8),
    axis.title = element_text(colour="black", size=10, face="bold"))
```

```{r, echo=F, warning=F, message=F}
ggarrange(sm_fr_length, rec_length, length_efs, sm_efs_efs, nrow=2, ncol=2)
```

<br>

<br>

### von Bertalanffy growth

Given the 'abnormal' von Bertalanffy growth patterns exhibited below, von Bertalanffy curves were fit to freshwater (juvenile) and marine (adult) growth stages separately to capture the two-step von B growth patterns. The freshwater growth stage included fry, age-1 and age-2 smolts, while the marine growth stage included age-3 (jack), age-4, age-5, and age-6 (where available) sockeye. These age cut-offs were chosen based on visual observations of growth patterns, and because von B models require a minimum of 3 years of length-at-age data to fit the model. 

```{r echo=F, warning=F, message=F}
# Facet plot of all length-at-age data over time (SLOW)
ggplot() +
  geom_line(data=vb.dat%>%group_by(vb_year0, vb_age)%>%summarize(med_l=median(vb_l, na.rm=T)), 
            aes(x=vb_age, y=med_l, group=vb_year0), size=0.65) +
  geom_point(data=vb.dat, aes(x=vb_age, y=vb_l, fill=sex), size=3, alpha=0.5, shape=21, colour="black") +
  scale_x_continuous(limits=c(0,6), breaks=seq(0,6,by=1)) +
  labs(x="Age", y="Length (mm)") +
  theme_bw() +
  theme(#axis.text=element_text(size=14, colour="black"),
    #axis.title=element_text(size=16, face="bold"),
    legend.position = c(0.93,0.03),
    panel.grid.minor = element_blank(),
    strip.text = element_text(size = 8),
    strip.background = element_rect(fill="white")) +
  facet_wrap(~vb_year0)
```

<br>

Requiring a minimum of 3 years of data for each model fitting process limited the available years of data to 15 years spanning 1986 to 2015 (see figure below). Subsequent years can be added once adult life stages have returned to spawn (the code to produce these results should be generalized to accommodate this in future). The resulting model fits for this subset of years are shown below. 

Start values for each parameter (Linf, k, t0) to initialize the von B models were automatically detected for each growth phase (freshwater/marine) and year using the *vbStarts* function and the *method="oldAge"* option, where Linf is detected based on the age of the oldest fish in each cohort. von B models were fit using *nls* and the typical *vb* function. Model parameters were extracted and used to generate predictions across a sequence of age ranges for each growth phase using *predict*. 95% confidence intervals were generated for each length-at-age prediction using *Boot*. 

```{r echo=F, message=F, warning=F}
ggplot() +
  geom_point(data=vb.juviadult.fitdat, aes(x=vb_age, y=vb_l, group=group), shape=21, size=2.5, stroke=1.3, alpha=0.2, fill="black", colour="black") +
  #geom_point(data=vb.dat.adult, aes(x=vb_age, y=vb_l), shape=21, size=2.5, stroke=1.3, alpha=0.2, fill="black", colour="black") +
  geom_ribbon(data=vb.fit.df, aes(x=vb_age, ymin=LCI, ymax=UCI, group=group), fill="red", alpha=0.2) +
  geom_line(data=vb.fit.df, aes(x=vb_age, y=pred_fit, group=group), size=0.7, colour="red") +
  labs(x="Age", y="Length (mm)", 
       caption="Fig . Fitted von Bertalanffy growth models with bootstrapped 95% confidence intervals for freshwater (fry and smolt) \nand marine (including jacks) growth phases for sockeye from Chilko River.") +
  facet_wrap(~vb_year0) +
  theme_bw() +
  theme(#axis.text = element_text(colour="black", size=12),
        #axis.title = element_text(face="bold", size=13),
        panel.grid.major = element_line(colour="gray82", size=0.1),
        panel.grid.minor = element_line(colour="gray82", size=0.1),
        plot.caption = element_text(hjust=0, face="italic", size=9))
```

<br>

```{r include=F, echo=F}
k.dat <- vonB.fits.CIs %>% filter(param=="k")
lm.k <- aov(estimate ~ group + vb_year0, data=k.dat)
summary(lm.k)
```

Preliminary examination indicates no significant variation in the growth rate coefficient (*k*) over time for either growth phase (*F*=0.85, *p*=0.61), but a significantly faster average freshwater growth rate (`r round(vonB.fits.CIs%>%filter(group=="Freshwater phase"&param=="k")%>%summarize(mean(estimate))%>%pull(), 2)` ± `r round(vonB.fits.CIs%>%filter(group=="Freshwater phase"&param=="k")%>%summarize(sd(estimate))%>%pull(), 2)`) than marine overall (`r round(vonB.fits.CIs%>%filter(group=="Marine phase"&param=="k")%>%summarize(mean(estimate))%>%pull(), 2)` ± `r round(vonB.fits.CIs%>%filter(group=="Marine phase"&param=="k")%>%summarize(sd(estimate))%>%pull(), 2)`; *F*=18.41, *p*=0.001, Two-way ANOVA; Fig below).  

```{r echo=F, message=F, warning=F}
ggplot(vonB.fits.CIs, aes(x=vb_year0, y=estimate, group=interaction(group,param), fill=group, colour=group)) +
  annotate("rect", xmin=1990, xmax=1993, ymin=-Inf, ymax=Inf, fill="red", alpha=0.2) + 
  geom_vline(xintercept=1988, linetype="solid", colour="red", size=1, alpha=0.2) +
  geom_errorbar(aes(x=vb_year0, ymax=UCI, ymin=LCI), width=0.2, size=0.7) +
  geom_point(shape=21, size=3, stroke=1, alpha=0.5) +
  scale_x_continuous(breaks=seq(1986,2015,by=2)) +
  facet_wrap(~param, nrow=3, scales = "free_y", labeller = as_labeller(c(`k`="k", `Linf`="Linf (mm)", `t0`="t0 (age)"))) +
  labs(x="Year", y="Parameter estimate", fill="Growth phase", caption="Fig . Paramter estimates and 95% confidence intervals for von Bertalanffy growth models fit to freshwater and marine \ngrowth phases of sockeye from the Chilko River. Red areas indicate years of lake fertilization.") +
  theme_bw() +
  theme(axis.text = element_text(colour="black"),
        axis.title = element_text(face="bold"),
        legend.position = "bottom", 
        plot.caption = element_text(hjust=0, face="italic", size=9)) +
  guides(colour=F)
```

<br>

<br>

<br>

<br>

<br>

<br>






































-------------------

-------------------

## Appendices  

-------------------

### Appendix 1: Data summaries 

```{r include=F, echo=F}
# set up
setwd("~/ANALYSIS/data")

#--------- DATA PART 1: Data sources -- 'smolt.abund.raw' always throws an error. just re-run this block again and it will work. 
smolt.bio.yrs <- excel_sheets("Daily Length (1986-2015).xlsx")
smolt.abund.raw <- read_excel("Chilko summary all years.xlsx", sheet="Annual outmigration")
esc.raw <- read_excel("DFO Sockeye Escapement All Years (June 2020).xlsx", sheet="SKAll")
fecund.raw <- read_excel("Sockeye Fecundity Database(2019VerifiedBB).xlsx", sheet="Data")
psc.raw <- read.csv("PSC_master.csv")
fry.raw <- read_excel("FryDB(Verified2019BB).xlsx", sheet="FryData")

#--------- CLEANING PART 1: Data sources
smolt_bio_yrs <- data.frame(year=as.numeric(smolt.bio.yrs), val="smolt biodata")

smolt_abund_yrs <- data.frame(year=as.numeric(smolt.abund.raw$`Smolt migration year`[1:68]), val="smolt abundance")

fry_bio_yrs <- fry.raw %>% 
  filter(Stream=="Chilko") %>%
  summarize(year=unique(YEAR), val="fry length & weight") %>% 
  print()

esc_yrs <- esc.raw %>% 
  filter(`CU Name` %in% c("Chilko - Summer", "Chilko - Early Summer"), !is.na(Total), !is.na(eff_fem)) %>%
  summarize(year=unique(Year), val="adult & ef esc") %>% 
  print()

fecund <- fecund.raw %>%
  filter(`Stock Name(stream)`=="Chilko River", !is.na(`Final Fecundity`)) %>%
  summarize(year=unique(Year), val="fecundity") %>% 
  print()

fecund_lengths <- fecund.raw %>% 
  filter(`Stock Name(stream)`=="Chilko River", !is.na(`Final Fecundity`), !is.na(`Std Length`), `Std Length`!=0.0) %>% 
  summarize(year=unique(Year), val="fecundity & length paired") %>%
  print()

age <- psc.raw %>% 
  filter(Stream_Shore%in%c("Chilko River", "Chilko Lake - South End", "Chilko Lake - North End"), TotalAge>=3, TotalAge<=5, Sex=="Female") %>% 
  summarize(year=unique(CollYear), val="age") %>% 
  print()

age_length <- psc.raw %>%
  filter(Stream_Shore%in%c("Chilko River", "Chilko Lake - South End", "Chilko Lake - North End"), TotalAge>=3, TotalAge<=5, POH!="0", POH!="#N/A",
    POH!="", STD!="0", STD!="#N/A", STD!="", Sex=="Female") %>% 
  summarize(year=unique(CollYear), val="age & length paired") %>%
  print()

alldat <- rbind(smolt_bio_yrs, smolt_abund_yrs, fry_bio_yrs, esc_yrs, fecund, fecund_lengths, age, age_length)
```

<br>

#### Chilko data summary ##

--------

DFO StAD data on Chilko juvenile and adult sockeye (Figure 1):

* Smolt abundance at migration
* Smolt length at migration
* Smolt age at migration
* Smolt migration timing (daily totals) - this may exist at finer resolution too
* Fry abundance, age, and size (sparse data)
* Total adult spawner abundance
* Effective female spawner abundance
* Male and female spawner length
* Fecundity
* Adult age (total and freshwater)
* Water level (continuous) and temperature (during programs)

Smolt length and age and fry length and age are currently stored in data formats that would require considerable work to bring into a useable format, especially for historical data. 

```{r, echo=F, warning=F}
ggplot(alldat, aes(x=val, y=year, group=year)) +
  annotate("rect", ymin=1990, ymax=1993, xmin=-Inf, xmax=Inf, fill="red", alpha=0.5) + 
  geom_hline(yintercept=1988, linetype="solid", colour="red", size=1, alpha=0.5) +
  geom_point(size=2.7, shape=21, fill="gray60", colour="black", stroke=1.1) +
  scale_y_continuous(breaks=seq(1938,2020,by=5)) +
  labs(y="", x="", caption="Figure . DFO Stock assessment time series for Chilko data types. No sex information was collected in conjunction with 'age' data in 1952 hence the gap. Lake fertilization years are coloured red (1988, 1990-1993). ")+
  coord_flip() +
  theme_bw() +
  theme(text = element_text(size=12, colour="black"),
    axis.text.x = element_text(angle=45, hjust=1))
```

&NewLine; 

Other types of data that may be held elsewhere: 

* Smolt freshwater growth rate (otoliths, scales or recaptures?)
* Smolt weight
* Smolt fat score
* Smolt growth rate (otoliths, scales or recaptures?) 
    - Smolt fork length in Lower Fraser/SoG
* Smolt survival during migration
    - Smolt abundance in Lower Fraser/SoG
* Smolt misc physiology - swim performance, hormones, respirometry, etc.
* Total growth rate over life (otoliths, scales) - PSC does not record to this level for adults but possible it could be obtained
* Adult fat score
* Adult misc physiology - swim performance, hormones, respirometry, etc.
* Fry abundance
* Lake productivity/food availability (especially during fertilization experimental years) - likely patchy at best
* Predator abundance (proxy or estimate of mortality rate)

Other data sources might be accessed through Environmental Watch Program, Hinch Lab, Mission Downstream (Tadey) or Strait of Georgia (Neville) programs. 

<br>

<br>

#### Other systems

Sparse fry data (Figure 2) and smolt data (below) exists for other systems if controls/comparisons are required:

* Cultus 1984, 1990-1991, 2000-2020
* Nautley 1999-2000, 2019
* South Thompson 2012-2013, 2016
* Historic (~1940-1950) Adams Lake, Bowron, Francois Lake, Horsefly, Lillooet Lake, Little River, Lower Shuswap, Portage Creek, Quesnel Lake, Seton Creek, South Thompson, Stuart Lake, Thompson

```{r, include=F}
fry_pops <- fry.raw %>% 
  group_by(Stream, YEAR) %>%
  summarize(n=n()) %>% 
  print()
```

```{r, echo=F, warning=F}
ggplot(fry_pops %>% filter(Stream!="Chilko"), aes(x=Stream, y=YEAR)) +
  geom_point(size=2.7, shape=21, fill="gray60", colour="black", stroke=1.1) +
  scale_y_continuous(breaks=seq(1938,2020,by=1)) +
  labs(y="", x="", caption="Figure . StA fry data excluding Chilko.")+
  coord_flip() +
  theme_bw() +
  theme(text = element_text(size=12, colour="black"),
    axis.text.x = element_text(angle=45, hjust=1))
```

<br>

<br>

<br>

----------

<br>

### Appendix 2: To weight, or not to weight 

The majority of smolts leave Chilko Lake as age-1 (>81% from 1986-2019). 

```{r, echo=F, warning=F, include=F}
#Figure x. Proportion of age-1 smolts leaving Chilko over time.
ggplot(data=smolt.df %>% group_by(smolt_year) %>% summarize(propn_age1 = age1_total/(age1_total+age2_total)), 
        aes(x=smolt_year, y=propn_age1)) +
  geom_line(size=1, colour="black") +
  geom_point(shape=21, size=3.5, colour="black", fill="white", stroke=1.5) +
  scale_x_continuous(breaks=seq(1986,2020, by=2)) +
  scale_y_continuous(limits=c(0.80,1), breaks=seq(0.80,1.0,by=0.05)) +
  labs(x="", y="% Age-1 smolts") +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=10),
    axis.title = element_text(colour="black", size=12, face="bold"))
```

<br>

Given substantial variability in nightly smolt migration and the non-random method of obtaining smolt length samples, it is recommended that smolt lengths be weighted by nighly abundance (S. Decker). Figure 3 shows minimal difference between weighted and unweighted average smolt fork lengths each year, but note significant deviance from zero-slope in many years (Figure 4 and Code 1).  

```{r, echo=F, warning=F}
#########
# FIG 3 #
#########
ggplot() +
  #annotate("text", x=2020, y=173, label="A") +
  annotate("rect", xmin=1990, xmax=1993, ymin=-Inf, ymax=Inf, fill="red", alpha=0.5) + 
  geom_vline(xintercept=1988, linetype="solid", colour="red", size=1, alpha=0.5) +
  geom_errorbar(data=smolt.df, aes(x=smolt_year, ymin=length_unweightavg_age1-length_unweightse_age1, ymax=length_unweightavg_age1+length_unweightse_age1), width=0, size=1, colour="gray60") +
  geom_line(data=smolt.df, aes(x=smolt_year, y=length_unweightavg_age1), colour="gray80", size=0.8, alpha=0.7) +
  geom_line(data=smolt.df, aes(x=smolt_year, y=length_weightavg_age1), colour="black", size=0.8, alpha=0.7) +
  geom_point(data=smolt.df, aes(x=smolt_year, y=length_unweightavg_age1), shape=21, colour="gray60", fill="gray80", size=2.5, stroke=1.2) +
  geom_point(data=smolt.df, aes(x=smolt_year, y=length_weightavg_age1), shape=21, colour="black", fill="#00b8ff", size=2.5, stroke=1.2) +
  scale_x_continuous(limits=c(1986,2020), breaks=seq(1986,2020,by=3)) +
  labs(x="", y="Age-1 smolt length (mm)", caption="Figure 3. Age-1 Chilko smolt fork lenghts, unweighted (light gray), and weighted-by-abundace (blue). Red shaded areas indicate years of lake fertilization. Error bars indicate one standard error and are given only for unweighted data. Note 2015 is included for comparison but due to high water an RST was used in place of the fence, which may result in size-selective bias. Following 2014 a 3-day smoothing window was also applied to daily weighted and unweighted length calculations.") +
  theme_bw() +
  theme(axis.text = element_text(colour="black", size=10),
    axis.title = element_text(colour="black", size=12, face="bold"))
```

<br>

```{r, echo=F, warning=F, message=F, include=F}
lm1 <- lm(smolt.lf[smolt.lf$age=="1"&smolt.lf$smolt_year=="2014",]$length_mm ~ smolt.lf[smolt.lf$age=="1" & smolt.lf$smolt_year=="2014",]$date)
r1 <- resid(lm1)
hist(r1)    # slight skew, center weighted
qqnorm(r1)  # bit of a tail 
qqline(r1)
plot(r1)
plot(lm1)

# grouped anova/lm (toggle 'lm' / 'aov' function if desired)
slope_tests <- smolt.lf %>% 
  filter(age%in%c(1,2)) %>%
  nest(-smolt_year, -age) %>% 
  mutate(fit = map(data, ~ lm(length_mm ~ date, data = .)),
         results = map(fit, glance)) %>% 
  unnest(results) %>%
  mutate(p.value = ifelse(p.value<0.01, "<0.01", round(p.value, 3))) %>%
  mutate_at(vars(c(r.squared, adj.r.squared, statistic)), funs(round(., 3))) %>%
  select(smolt_year, age, r.squared, adj.r.squared, sigma, p.value, df, nobs) %>%
  mutate(sig = ifelse(p.value < 0.05, "sig", "not sig")) %>%
  rename(t.stat = sigma) %>%
  print()
```

Of the smolt cohorts examined so far (`r min(smolt.lf$smolt_year)`-`r max(smolt.lf$smolt_year)`), most age-1 smolt-years (`r round(slope_tests %>% filter(age==1) %>% group_by(sig) %>% summarize(n=n()) %>% mutate(propn=n/sum(n)) %>% {.[2,3]}*100, 1)`%) show a significant change (usually increase) in length over the migration period (Linear regression p < 0.05), even though the linear regression slopes are typically near-zero (but variable, `r round(slope_tests %>% filter(age==1) %>% summarize(mean(r.squared)) %>% {.[1,1]}, 3)` +/- `r round(slope_tests %>% filter(age==1) %>% summarize(sd(r.squared)) %>% {.[1,1]}, 3)`). This is compared to `r round(slope_tests %>% filter(age==2) %>% group_by(sig) %>% summarize(n=n()) %>% mutate(propn=n/sum(n)) %>% {.[2,3]}*100, 1)`% of age-2 smolt-years exhibiting a significant change in length over the migration period (average r^2 = `r round(slope_tests %>% filter(age==2) %>% summarize(mean(r.squared)) %>% {.[1,1]}, 3)` +/- `r round(slope_tests %>% filter(age==2) %>% summarize(sd(r.squared)) %>% {.[1,1]}, 3)`; Code 1 and Figure 4)

```{r, echo=F, warning=F, include=F, eval=F}
### xxx OLD FIG - Daily smolt length (mm) in the most recent 5 years expressed as a) boxplot with medians and quartiles, and b) point size scaled by frequency of observations. Note different x- and y- axis limits for all plots.
ggplot(smolt.lf%>%filter(!is.na(age)), aes(x=as.Date(yday, origin=as.Date("1970-01-01")), y=length_mm, group=interaction(age, yday))) +
  #geom_bar(stat="identity", colour="black") +
  #geom_point() +
  #geom_errorbar(aes(x=as.Date(yday, origin=as.Date("1970-01-01")), ymin=mean_length-sd, ymax=mean_length+sd)) +
  geom_boxplot(aes(fill=age), alpha=0.8, width=1) +
  scale_x_date(date_labels="%b %d") +
  labs(x="", y="Length (mm)") +
  #facet_wrap(~smolt_year, scales="free") +     # too many yeras - reaches limit
  theme_bw() +
  theme(legend.position = c(0.8,0.2))

ggplot(smolt.lf%>%filter(!is.na(age)), aes(x=as.Date(yday, origin=as.Date("1970-01-01")), y=length_mm, size=freq, group=interaction(age, yday))) +
  geom_point(aes(fill=age), alpha=0.2, shape=21, stroke=0.5) +
  scale_x_date(date_labels="%b %d") +
  scale_size_continuous(range=c(2,8)) +
  labs(x="", y="Length (mm)") +
  #facet_wrap(~smolt_year, scales="free") +     # too many yeras - reaches limit
  theme_bw() +
  theme(legend.position = c(0.85,0.2),
    legend.box="horizontal") +
  guides(fill = guide_legend(override.aes = list(size = 3))) 

### xxx OLD FIG - 3D plot of smolt length (mm) frequency over time during the 2014 outmigration. (would need varnames refreshed)
# clean, pivot to wide matrix format 
#smolt.lf_w14_1 <- smolt.lf %>%
#  filter(smolt_year==2014, age==1) %>%
#  arrange(yday, length_mm) %>%
#  select(yday, length_mm, freq) %>%
#  pivot_wider(names_from=length_mm, values_from=freq) %>%
#  column_to_rownames(var="yday") %>%
#  print()

# replace 0s with NAs to make plot clearer
#smolt.lf_w14_1[smolt.lf_w14_1==0]=NA

# convert to matrix format
#smolt.lf_w14_1 <- data.matrix(smolt.lf_w14_1, rownames.force = NA)

# x and y value sequences for plot
#rnameseq <- as.numeric(row.names(smolt.lf_w14_1))
#cnameseq <- as.numeric(colnames(smolt.lf_w14_1))

# 3D PLOT!
#hist3D(x=rnameseq, y=cnameseq, z=smolt.lf_w14_1, scale=F, expand=0.23, bty="g", phi=25,
#        col=jet.col(100, alpha=1), border="black", shade=0, theta=40,
#        space=0, ticktype="detailed", d=2, xlab = "Date", ylab = "Length (mm)", zlab = "Frequency", main="Chilko 2014")
```

```{r, warning=F, echo=F, message=F}
#########
# FIG 4 #
######### broken up into several multi-panel plots for visualization
# *Fig 4. Age-1 and -2 Chilko smolt length over time for most recent 20 years of data. Points indicate means. Violin widths indicate data density. # Note different y-axis limits for each plot and 2015 was an RST-only year (no fence).*

ggplot(smolt.lf%>%filter(age%in%c(1,2), smolt_year%in%c(2016:2019)), aes(x=as.Date(yday, origin=as.Date("1970-01-01")), y=length_mm)) +
  geom_violin(aes(fill=age, group=interaction(age, yday)), alpha=0.7, colour="transparent") +
  geom_smooth(aes(group=age, colour=age), method="lm") +
  stat_summary(aes(fill=age), fun=mean, geom="point", shape=21, colour="black") +
  labs(x="", y="Length (mm)") +
  facet_wrap(~smolt_year, scales="free") +
  theme_bw() +
  theme(legend.position = "bottom") +
  stat_cor(aes(group=age, colour=age, label=..rr.label..), size=3, label.y=c(67,67), label.x=c(108,120), show.legend = F) +
  stat_cor(aes(group=age, colour=age, label=..p.label..), size=3, label.y=c(60,60), label.x=c(108,120), show.legend = F)

ggplot(smolt.lf%>%filter(age%in%c(1,2), smolt_year%in%c(2010:2015)), aes(x=as.Date(yday, origin=as.Date("1970-01-01")), y=length_mm)) +
  geom_violin(aes(fill=age, group=interaction(age, yday)), alpha=0.7, colour="transparent") +
  geom_smooth(aes(group=age, colour=age), method="lm") +
  stat_summary(aes(fill=age), fun=mean, geom="point", shape=21, colour="black") +
  labs(x="", y="Length (mm)") +
  facet_wrap(~smolt_year, scales="free") +
  theme_bw() +
  theme(legend.position = c(0.8,0.2)) +
  stat_cor(aes(group=age, colour=age, label=..rr.label..), size=3, label.y=c(67,67), label.x=c(108,120), show.legend = F) +
  stat_cor(aes(group=age, colour=age, label=..p.label..), size=3, label.y=c(60,60), label.x=c(108,120), show.legend = F)

ggplot(smolt.lf%>%filter(age%in%c(1,2), smolt_year%in%c(2005:2009)), aes(x=as.Date(yday, origin=as.Date("1970-01-01")), y=length_mm)) +
  geom_violin(aes(fill=age, group=interaction(age, yday)), alpha=0.7, colour="transparent") +
  geom_smooth(aes(group=age, colour=age), method="lm") +
  stat_summary(aes(fill=age), fun=mean, geom="point", shape=21, colour="black") +
  labs(x="", y="Length (mm)") +
  facet_wrap(~smolt_year, scales="free") +
  theme_bw() +
  theme(legend.position = c(0.8,0.2)) +
  stat_cor(aes(group=age, colour=age, label=..rr.label..), size=3, label.y=c(67,67), label.x=c(108,120), show.legend = F) +
  stat_cor(aes(group=age, colour=age, label=..p.label..), size=3, label.y=c(60,60), label.x=c(108,120), show.legend = F) 

ggplot(smolt.lf%>%filter(age%in%c(1,2), smolt_year%in%c(2000:2004)), aes(x=as.Date(yday, origin=as.Date("1970-01-01")), y=length_mm)) +
  geom_violin(aes(fill=age, group=interaction(age, yday)), alpha=0.7, colour="transparent") +
  geom_smooth(aes(group=age, colour=age), method="lm") +
  stat_summary(aes(fill=age), fun=mean, geom="point", shape=21, colour="black") +
  labs(x="", y="Length (mm)") +
  facet_wrap(~smolt_year, scales="free") +
  theme_bw() +
  theme(legend.position = c(0.8,0.2)) +
  stat_cor(aes(group=age, colour=age, label=..rr.label..), size=3, label.y=c(67,67), label.x=c(108,120), show.legend = F) +
  stat_cor(aes(group=age, colour=age, label=..p.label..), size=3, label.y=c(60,60), label.x=c(108,120), show.legend = F) 
```

<br>

*Code 1. Linear models examining the effect of 'day' on smolt length for each year and age.*

```{r, echo=F, warning=F, message=F}
slope_tests %>% print(n=1000)
```

&NewLine;

&NewLine;

&NewLine;





















